---
title: "Caloosahatchee Conditions Report -<br>Stakeholder Data Sources"
output: 
  html_document: 
    toc: yes
    includes:
      after_body: footer.html
editor_options: 
  chunk_output_type: console
---
***

`r paste("Updated",as.POSIXct(Sys.time(),"%Y-%m-%d %H:%M",tz=""))`

***

<font size=2>Additional information on Lake Okeechobee Stage and recession rate can be found on our companion site -  [Link](https://sccf-tech.github.io/CRE_Conditions/report/CRE_REPORT.html)</font>

***

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE,
                      message=FALSE,
                      warning=FALSE)

## Libraries
library(AnalystHelper)
library(reshape)
library(plyr)
library(zoo)
library(rvest)
library(lubridate)
library(flextable)
library(magrittr)
library(grid)
library(RcppRoll)
##

dates=seq(date.fun(date.fun(Sys.Date())-ddays(13)),date.fun(Sys.Date()),"1 days")

```

```{r data, include=F}
## Lake Okeechobee Report
LO.url="https://w3.saj.usace.army.mil/h2o/reports/r-oke.html"
webpage=read_html(LO.url)
node.val=html_nodes(webpage,"pre")

LO.text.vals=html_text(node.val)
LO.report=strsplit(as.character(LO.text.vals),"\n")
LO.report

grep("*Okeechobee Lake Elevation",LO.report[[1]])


tmp1=data.frame(t(sapply(strsplit(LO.report[[1]][266:279],"\\s+"),c)))
colnames(tmp1)=c("day","month","year","S77","S77_ds","S78","S79")
tmp1$Date=with(tmp1,date.fun(paste(year,month,day),form="%Y %B %d"))
tmp1[,4:7]=sapply(tmp1[,4:7],as.numeric)

tmp2=data.frame(t(sapply(strsplit(LO.report[[1]][285:298],"\\s+"),c)))
colnames(tmp2)=c("day","month","year","S310","S351","S352","S354","L8")
tmp2$Date=with(tmp2,date.fun(paste(year,month,day),form="%Y %B %d"))
tmp2[,4:8]=sapply(tmp2[,4:8],as.numeric)

tmp3=data.frame(t(sapply(strsplit(LO.report[[1]][304:317],"\\s+"),c)))
colnames(tmp3)=c("day","month","year","S308","S308_ds","S80")
tmp3$Date=with(tmp3,date.fun(paste(year,month,day),form="%Y %B %d"))
tmp3[,4:6]=sapply(tmp3[,4:6],as.numeric)

q.dat=cbind(tmp1[,c(8,4:7)],tmp2[,c(4:8)],tmp3[,c(4:6)])

## Preferred Structures
str.url="https://w3.saj.usace.army.mil/h2o/reports/r-lonin.html"
webpage=read_html(str.url)
node.val=html_nodes(webpage,"pre")

str.text.vals=html_text(node.val)
str.report=strsplit(as.character(str.text.vals),"\n")
str.report

pref.struct=data.frame(t(sapply(strsplit(str.report[[1]][21:34],"\\|"),c)))
pref.struct
colnames(pref.struct)=c("Date","LONIN_cfs","STORAGE_cfs","S77","S308","S351","S352","S354","L8")
pref.struct[,2:9]=sapply(pref.struct[,2:9],as.numeric)
pref.struct$Date=date.fun(pref.struct$Date,form="%d %B %Y")
pref.struct[,2:9]=cfs.to.acftd(pref.struct[,2:9])

## Discharge data for lake and estuaries
q.dat=merge(pref.struct[,c("Date","S77","S308","L8",'S351',"S352","S354")],
q.dat[,c("Date","S78","S79","S310","S80")],"Date")

## Maps and Archived data
map.q=data.frame()
for(i in 1:length(dates)){
  map.url=paste0("https://w3.saj.usace.army.mil/h2o/reports/StatusDaily/archive/",format(dates[i],"%m%d"),"/StatusDaily.htm")
  mapdata=readLines(map.url)
  val=grep("CA1IN",mapdata)
  WCA1=strsplit(strsplit(mapdata[val],"\\s+")[[1]][13],"</div>")[[1]][1]
  
  val=grep("CA2IN",mapdata)
  WCA2=strsplit(strsplit(mapdata[val],"\\s+")[[1]][13],"</div>")[[1]][1]
  
  val=grep("CA3IN",mapdata)
  WCA3=strsplit(strsplit(mapdata[val],"\\s+")[[1]][13],"</div>")[[1]][1]
  
  val=grep("S12",mapdata)
  ENP=strsplit(strsplit(mapdata[val],"\\s+")[[1]][8],"</div>")[[1]][1]
  
  date.val=dates[i]-ddays(1)
  rslt=data.frame(Date=date.val,WCA1=as.numeric(WCA1),WCA2=as.numeric(WCA2),WCA3=as.numeric(WCA3),ENP=as.numeric(ENP))
  map.q=rbind(map.q,rslt)
  print(i)
}

map.q[,2:5]=cfs.to.acftd(map.q[,2:5])

q.dat=merge(q.dat,map.q,"Date")
# q.dat[q.dat<0]<-NA

```

```{r table1}
vars=c("Date","S77","S78","S79","S310","S351","S352","S354","L8","S308","S80","WCA1","WCA2","WCA3","ENP")
date.7day=seq(date.fun(date.fun(Sys.Date())-ddays(7)),date.fun(Sys.Date()),"1 days")

q.dat.7day=subset(q.dat,Date%in%date.7day)[,vars]
meanQ=cbind(data.frame(Statistic="Average"),data.frame(t(apply(q.dat.7day[,2:15],2,mean,na.rm=T))))
colnames(meanQ)<-c("Statistic",vars[2:length(vars)])
totalQ=cbind(data.frame(Statistic="Total"),data.frame(t(apply(q.dat.7day[,2:15],2,sum,na.rm=T))))
colnames(totalQ)<-c("Statistic",vars[2:length(vars)])
sumstats=rbind(meanQ,totalQ)


meanQ.14=cbind(data.frame(Statistic="Average"),data.frame(t(apply(q.dat[,vars[2:length(vars)]],2,mean,na.rm=T))))
colnames(meanQ.14)<-c("Statistic",vars[2:length(vars)])
totalQ.14=cbind(data.frame(Statistic="Total"),data.frame(t(apply(q.dat[,vars[2:length(vars)]],2,sum,na.rm=T))))
colnames(totalQ.14)<-c("Statistic",vars[2:length(vars)])

sumstats14=rbind(meanQ.14,totalQ.14)


q.dat.7day=q.dat.7day[match(q.dat.7day$Date,rev(q.dat.7day$Date)),]
q.dat=q.dat[match(q.dat$Date,rev(q.dat$Date)),]

cap.val="Daily discharge volume in Acre-Feet per day for the last 14-days. Data Source: USACE"
q.dat[,vars]%>%
  flextable()%>%
  colformat_datetime(j=1,fmt_date="%m-%d")%>%
  colformat_double(j=2:15,big.mark = "",digits=0)%>%
  align(j=2:15,part="all",align="center")%>%
  padding(padding=1,part="all")%>%
  font(fontname="Times New Roman",part="all")%>%
  fontsize(size=10,part="body")%>%
  fontsize(size=12,part="header")%>%
  add_header_lines(values=cap.val)%>%
  align(align="center",part="header")%>%fontsize(size=12,part="header")%>%font(fontname = "Times New Roman",part="all")
  # footnote(i=1,j=1,value=as_paragraph("Negative flow values omitted from this table and statistical summaries below."),ref_symbols =c(" "),part="header")
```


```{r}
library(downloadthis)

q.dat%>%
  download_this(
    output_name = "Discharge7day",
    output_extension = ".xlsx",
    button_label = "Download Discharge as .xlsx",
    button_type = "primary",
    has_icon = TRUE,
    icon = "fa fa-file-excel"
  )
```

```{r}
cap.val="Average and total discharge volume in Acre-Feet per day for the last 7-days. Data Source: USACE"
sumstats%>%
  flextable()%>%
  colformat_double(j=2:15,big.mark = "",digits=0)%>%
  align(j=2:15,part="all",align="center")%>%
  padding(padding=1,part="all")%>%
  font(fontname="Times New Roman",part="all")%>%
  fontsize(size=10,part="body")%>%
  fontsize(size=12,part="header")%>%
  add_header_lines(values=cap.val)%>%
  align(align="center",part="header")%>%fontsize(size=12,part="header")%>%font(fontname = "Times New Roman",part="all")

```


```{r}
cap.val="Average and total discharge volume in Acre-Feet per day for the last 14-days. Data Source: USACE"
sumstats14%>%
  flextable()%>%
  colformat_double(j=2:15,big.mark = "",digits=0)%>%
  align(j=2:15,part="all",align="center")%>%
  padding(padding=1,part="all")%>%
  font(fontname="Times New Roman",part="all")%>%
  fontsize(size=10,part="body")%>%
  fontsize(size=12,part="header")%>%
  add_header_lines(values=cap.val)%>%
  align(align="center",part="header")%>%fontsize(size=12,part="header")%>%font(fontname = "Times New Roman",part="all")

```

```{r}
q.from.Lake=sum(totalQ[,c("S77","S310","S351","S352","S354","L8","S308")])
S77q=sum(totalQ[,c("S77")])
S77q.per=round(S77q/q.from.Lake*100,0)

S308q=sum(totalQ[,c("S308")])
S308q.per=round(S308q/q.from.Lake*100,0)

S310q=sum(totalQ[,c("S310")])
S310q.per=round(S310q/q.from.Lake*100,0)

L8q=sum(totalQ[,c("L8")])
L8q.per=round(L8q/q.from.Lake*100,0)

EAAq=sum(totalQ[,c("S351","S352","S354")])
EAAq.per=round(EAAq/q.from.Lake*100,0)


```

**Lake Flows:** In the past 7 days `r ifelse(min(apply(q.dat.7day,1,FUN=function(x)min(x,na.rm=T)))<0,"a net flow of","")` **`r format(round(q.from.Lake,0),big.mark=",")`**  AF were discharged from Lake Okeechobee, with **`r format(round(S77q,0),big.mark=",")` AF (`r S77q.per`%)** to the Caloosahatchee through **S-77**, **`r format(round(S308q,0),big.mark=",")` AF (`r S308q.per`%)** to the St. Lucie River through **S-308**, **`r format(round(S310q,0),big.mark=",")` AF (`r S310q.per`%)** through **S-310** in Clewiston, **`r format(round(L8q,0),big.mark=",")` AF (`r L8q.per`%)** through **C-10A** to the L-8 canal, and **`r format(round(EAAq,0),big.mark=",")` AF (`r EAAq.per`%)** to the EAA through **S-351, S-352, and S-354**. Water conservation areas received flows of **`r format(round(sum(totalQ[,c("WCA1")]),0),big.mark=",")` AF**, **`r format(round(sum(totalQ[,c("WCA2")]),0),big.mark=",")` AF**, and **`r format(round(sum(totalQ[,c("WCA3")]),0),big.mark=",")` AF** at **WCA1, WCA2, and WCA3**,respectively. Everglades National Park received **`r format(round(sum(totalQ[,c("ENP")]),0),big.mark=",")` AF**.

<br>

<div class="row">
<div class="col-md-6">
**Lake Okeechobee Level: `r paste0(strsplit(LO.report[[1]][11],"\\s+")[[1]][5]," ft"," (",strsplit(LO.report[[1]][13],"  Currently in ")[[1]][2],")")`**

**Lake Okeechobee Inflow: `r paste(strsplit(LO.report[[1]][45],"\\s+")[[1]][3],"cfs")`**

</div>

<div class="col-md-6">
**Last Week: `r paste(strsplit(LO.report[[1]][200],"\\s+")[[1]][9],"ft")`**

**Lake Okeechobee Outflow: `r paste(strsplit(LO.report[[1]][52],"\\s+")[[1]][3],"cfs")`**
</div>
</div>

```{r}
S77.dat=readLines("https://w3.saj.usace.army.mil/h2o/reports/r-s77m.html")
S77.dat=data.frame(t(sapply(strsplit(S77.dat[11:17],"\\s+"),c)))
colnames(S77.dat)=c("Date","HW","TW","Q","Precip","WndDir","WndSp","Locks","Bar.Hg","Bar.mBar","Evap","Man.Prec")
S77.dat$Date=date.fun(S77.dat$Date,form="%d%B%y")
S77.dat[,2:12]=sapply(S77.dat[,2:12],as.numeric)
S77.dat$SITE="Moore Haven (S77)"

S78.dat=readLines("https://w3.saj.usace.army.mil/h2o/reports/r-s78m.html")
S78.dat=data.frame(t(sapply(strsplit(S78.dat[11:17],"\\s+"),c)))
colnames(S78.dat)=c("Date","HW","TW","Q","Precip","WndDir","WndSp","Locks","Bar.Hg","Bar.mBar","Man.Prec")
S78.dat$Date=date.fun(S78.dat$Date,form="%d%B%y")
S78.dat[,2:11]=sapply(S78.dat[,2:11],as.numeric)
S78.dat$SITE="Ortona (S78)"

S79.dat=readLines("https://w3.saj.usace.army.mil/h2o/reports/r-s79m.html")
S79.dat=data.frame(t(sapply(strsplit(S79.dat[11:17],"\\s+"),c)))
colnames(S79.dat)=c("Date","HW","TW","Q","Precip","WndDir","WndSp","Locks","Bar.Hg","Bar.mBar","Cl","Man.Prec")
S79.dat$Date=date.fun(S79.dat$Date,form="%d%B%y")
S79.dat[,2:12]=sapply(S79.dat[,2:12],as.numeric)
S79.dat$SITE="WP Franklin (S79)"

vars=c("Date","SITE","Man.Prec")
RF.dat=rbind(S77.dat[,vars],S78.dat[,vars],S79.dat[,vars])

```

<!-- https://holtzy.github.io/Pimp-my-rmd/#several_columns -->
<div class="row">
<div class="col-md-3">
**Weekly Rainfall Total:** 
</div>
<div class="col-md-3">
WP Franklin **`r with(S79.dat,ifelse(sum(is.na(Man.Prec))!=0,paste("\u2265",format(sum(Man.Prec,na.rm=T),nsmall=2)),format(sum(Man.Prec,na.rm=T),nsmall=2)))`"**
</div>
<div class="col-md-3">
Ortona **`r with(S78.dat,ifelse(sum(is.na(Man.Prec))!=0,paste("\u2265",format(sum(Man.Prec,na.rm=T),nsmall=2)),format(sum(Man.Prec,na.rm=T),nsmall=2)))`"**
</div>
<div class="col-md-3">
Moore Haven **`r with(S77.dat,ifelse(sum(is.na(Man.Prec))!=0,paste("\u2265",format(sum(Man.Prec,na.rm=T),nsmall=2)),format(sum(Man.Prec,na.rm=T),nsmall=2)))`"**
</div>
</div>

```{r}
RF.dat%>%
  download_this(
    output_name = "RF7day",
    output_extension = ".xlsx",
    button_label = "Download Rainfall as .xlsx",
    button_type = "primary",
    has_icon = TRUE,
    icon = "fa fa-file-excel"
  )
```

***
```{r, echo=FALSE,fig.width=6,fig.height=4,fig.align='center'}
# RECON.dates=date.fun(c(Sys.Date()-duration(6, "months"),date.fun(Sys.Date())))
RECON.dates=date.fun(c(Sys.Date()-duration(1, "years"),date.fun(Sys.Date())))
# RECON.dates
dates.fill=data.frame(DATE=seq(RECON.dates[1],RECON.dates[2],"1 days"),fill=1)

dat.recon=read.csv("C:/Julian_LaCie/_Github/CRE_Conditions/Data/stakeholder/chart.csv")
dat.recon$DateTime=date.fun(dat.recon$DateTime,form="%F %X")
dat.recon$Date=date.fun(dat.recon$DateTime)
colnames(dat.recon)=c("DATETIME","Sal","DATE")
dat.recon$source="RECON"
# RECON.dates=date.fun(range(dat$DateTime))
# da.dat.recon=ddply(dat.recon,"DATE",summarise,mean.val=mean(Sal,na.rm=T))
# da.dat.recon$Sal.30d=with(da.dat.recon,c(rep(NA,29),rollapply(mean.val,width=30,FUN=function(x)mean(x,na.rm=T))))

## replace RECON till fix
bk.dbkeys.surf=data.frame(depth="Surface",
                         SITE=c(rep("FORTMYERSM",2)),
                         param=rep(c("WT","SPC"),1),
                         DBKEY=c("88287","88292")
                         )
dat=data.frame()
for(i in 1:nrow(bk.dbkeys.surf)){
tmp=DBHYDRO_breakpoint(RECON.dates[1],RECON.dates[2],bk.dbkeys.surf$DBKEY[i])  
tmp$DBKEY=as.character(bk.dbkeys.surf$DBKEY[i])
dat=rbind(dat,tmp)
# print(i)
}
dat=merge(dat,bk.dbkeys.surf,"DBKEY")
dat.xtab=data.frame(cast(dat,SITE+DATETIME+DATE~param,value="Data.Value",mean))
dat.xtab$Sal=with(dat.xtab,SalinityCalc(SPC,WT))
dat.xtab$source="SFWMD"
# da.dat=ddply(dat.xtab,"DATE",summarise,mean.val=mean(Sal,na.rm=T))
# da.dat$Sal.30d=with(da.dat,c(rep(NA,29),rollapply(mean.val,width=30,FUN=function(x)mean(x,na.rm=T))))


vars=c("DATETIME","DATE","Sal","source")
dat.xtab.comb=rbind(dat.xtab[,vars],dat.recon[,vars])
dat.xtab2=cast(dat.xtab.comb,DATETIME+DATE~source,value="Sal",mean)
dat.xtab2$Sal=with(dat.xtab2,ifelse(is.na(SFWMD)==T,RECON,SFWMD))
dat.xtab2=merge(dat.xtab2,dates.fill,"DATE",all.y=T)
da.dat=ddply(dat.xtab2,"DATE",summarise,mean.val=mean(Sal,na.rm=T))
da.dat$Sal.30d=with(da.dat,c(rep(NA,29),rollapply(mean.val,width=30,FUN=function(x)mean(x,na.rm=T))))
#da.dat=merge(da.dat,dates.fill,"DATE",all.y=T)

cal.q=DBHYDRO_daily(RECON.dates[1]-duration(2,"months"),RECON.dates[2],"DJ237")
cal.q$Date=date.fun(cal.q$Date)
cal.q$Q.30=with(cal.q,c(rep(NA,29),rollapply(Data.Value,width=30,FUN=function(x)mean(x,na.rm=T))))

ylim.val=c(0,30);by.y=5;ymaj=seq(ylim.val[1],ylim.val[2],by.y);ymin=seq(ylim.val[1],ylim.val[2],by.y/2)
xlim.val=c(date.fun(RECON.dates[2]-duration(6, "months")),date.fun(RECON.dates[2]+duration(15,"days")));xmaj=seq(xlim.val[1],xlim.val[2],by="2 months ");xmin=seq(xlim.val[1],xlim.val[2],by="1 months")

par(family="serif",cex.axis=1.2,mar=c(3.5,1.75,1,4.5),oma=c(0.5,3,1,2));
plot(Sal~DATETIME,dat.xtab,type="n",ylim=ylim.val,xlim=xlim.val,xaxs="i",yaxs="i",xaxt="n",yaxt="n",xlab=NA,ylab=NA)
abline(h=ymaj,v=xmaj,lty=3,col="grey")
# with(dat,lines(DateTime,Sal,lty=1,col="blue",lwd=1.5))
# with(da.dat,lines(Date,Sal.30d,lty=1,col="darkolivegreen3",lwd=2))
with(dat.xtab2,lines(DATETIME,Sal,lty=1,col="blue",lwd=2))
with(da.dat,lines(DATE,Sal.30d,lty=1,col="darkolivegreen3",lwd=4))
axis_fun(1,xmaj,xmin,NA)
axis_fun(2,ymaj,ymin,ymaj)
text(xmaj,-1.5,format(xmaj,"%m/%d/%y"),srt=-45,xpd=NA,adj=0,cex=0.95)
mtext(side=2,line=2,"Salinity (PSU)")
mtext(side=1,line=3,"Date (MM/DD/YY)")
ylim.val=c(0,20000);by.y=4000;ymaj=seq(ylim.val[1],ylim.val[2],by.y);ymin=seq(ylim.val[1],ylim.val[2],by.y/2)
par(new=T);plot(Data.Value~Date,cal.q,type="n",ylim=ylim.val,xlim=xlim.val,xaxs="i",yaxs="i",xaxt="n",yaxt="n",xlab=NA,ylab=NA)
with(cal.q,lines(Date,Data.Value,lwd=2,col="black"))
with(cal.q,lines(Date,Q.30,lwd=4,col="indianred1"))
# abline(h=475,lty=2,col="red")
axis_fun(4,ymaj,ymin,ymaj)
mtext(side=4,line=3.25,"Discharge (cfs)")
mtext(side=3,"Surface Salinity at Fort Myers Yacht Basin")

# legend("topright",
#        legend=c("Hourly Salinity","30-Day Avg Sal","S79 Daily Discharge","30-d Avg Discharge","MFL (40E-8.221(2) FAC)"),
#        lty=c(1,1,1,1,2),lwd=c(1,2,1,2,1),
#        col=c("blue","darkolivegreen3","black","indianred1","red"),
#        ncol=1,cex=0.8,bty="n",y.intersp=1,x.intersp=1,xpd=NA,xjust=0.5)
legend("topright",
       legend=c("Hourly Salinity","30-Day Avg Sal","S79 Daily Discharge","30-d Avg Discharge"),
       lty=c(1,1,1,1),lwd=c(1,2,1,2),
       col=c("blue","darkolivegreen3","black","indianred1"),
       ncol=1,cex=0.8,bty="n",y.intersp=1,x.intersp=1,xpd=NA,xjust=0.5)
logo=png::readPNG("c:/Julian_LaCie/_GitHub/CRE_Conditions/report/Logo no Background.png")
grid.raster(logo,x=0.16,y=0.9,just=c("left","top"),width=unit(1.25,"inches"))
```

<font size=2><center>Fort Myers Yacht Basin salinity (SCCF-RECON) and S79 discharge (SFWMD) data for the last six months.</center></font>
<font size=3 color="red"><center>Data are provisional and subject to change.</center></font>


```{r,echo=FALSE,fig.width=6,fig.height=4,fig.align='center'}
seq.30d=seq(date.fun(RECON.dates[2]-duration(30,"days")),date.fun(RECON.dates[2]+duration(15,"days")),"1 days")

max.ylim.2=round(max(subset(cal.q,Date%in%seq.30d)$Data.Value,na.rm=T)+max(subset(cal.q,Date%in%seq.30d)$Data.Value,na.rm=T)*0.25,-3)

ylim.val=c(0,30);by.y=5;ymaj=seq(ylim.val[1],ylim.val[2],by.y);ymin=seq(ylim.val[1],ylim.val[2],by.y/2)
xlim.val=c(date.fun(RECON.dates[2]-duration(30,"days")),date.fun(RECON.dates[2]+duration(15,"days")));xmaj=seq(xlim.val[1],xlim.val[2],by="14 days ");xmin=seq(xlim.val[1],xlim.val[2],by="1 days")

par(family="serif",cex.axis=1.2,mar=c(3.5,1.75,1,4.5),oma=c(0.5,3,1,2));
plot(Sal~DATETIME,dat.xtab,type="n",ylim=ylim.val,xlim=xlim.val,xaxs="i",yaxs="i",xaxt="n",yaxt="n",xlab=NA,ylab=NA)
abline(h=ymaj,v=xmaj,lty=3,col="grey")
# with(dat,lines(DateTime,Sal,lty=1,col="blue",lwd=1.5))
# with(da.dat,lines(Date,Sal.30d,lty=1,col="darkolivegreen3",lwd=2))
with(dat.xtab2,lines(DATETIME,Sal,lty=1,col="blue",lwd=2))
with(da.dat,lines(DATE,Sal.30d,lty=1,col="darkolivegreen3",lwd=4))
axis_fun(1,xmaj,xmin,NA)
axis_fun(2,ymaj,ymin,ymaj)
text(xmaj,-1.5,format(xmaj,"%m/%d/%y"),srt=-45,xpd=NA,adj=0,cex=0.95)
mtext(side=2,line=2,"Salinity (PSU)")
mtext(side=1,line=3,"Date (MM/DD/YY)")
ylim.val=c(0,max.ylim.2);by.y=max.ylim.2/4;ymaj=seq(ylim.val[1],ylim.val[2],by.y);ymin=seq(ylim.val[1],ylim.val[2],by.y/2)
par(new=T);plot(Data.Value~Date,cal.q,type="n",ylim=ylim.val,xlim=xlim.val,xaxs="i",yaxs="i",xaxt="n",yaxt="n",xlab=NA,ylab=NA)
with(cal.q,lines(Date,Data.Value,lwd=2,col="black"))
with(cal.q,lines(Date,Q.30,lwd=4,col="indianred1"))
abline(h=475,lty=2,col="red")
text(date.fun(xlim.val[2]-ddays(6)),475,"MFL (30d Q)",font=2,cex=0.75,col="red",pos=3)
axis_fun(4,ymaj,ymin,ymaj)
mtext(side=4,line=3.25,"Discharge (cfs)")
mtext(side=3,"Surface Salinity at Fort Myers Yacht Basin")

legend("topright",
       legend=c("Hourly Salinity","30-Day Avg Sal","S79 Daily Discharge","30-d Avg Discharge","MFL (40E-8.221(2) FAC)"),
       lty=c(1,1,1,1,2),lwd=c(1,2,1,2,1),
       col=c("blue","darkolivegreen3","black","indianred1","red"),
       ncol=1,cex=0.8,bty="n",y.intersp=1,x.intersp=1,xpd=NA,xjust=0.5)
logo=png::readPNG("c:/Julian_LaCie/_GitHub/CRE_Conditions/report/Logo no Background.png")
grid.raster(logo,x=0.16,y=0.9,just=c("left","top"),width=unit(1.25,"inches"))

```

<font size=2><center>Fort Myers Yacht Basin salinity (SCCF-RECON) and S79 discharge (SFWMD) data for the last last 30 days.</center></font>
<font size=3 color="red"><center>Data are provisional and subject to change.</center></font>


***
```{r, out.width = '100%', out.height='400px' }
library(plotly)
xlim.val.ly=c(RECON.dates[1],date.fun(RECON.dates[2]+duration(15,"days")))

plot_ly(x=~DATETIME,y=~round(Sal,1),
        data=dat.xtab2,
        type="scatter",mode="lines",color=I(adjustcolor('blue',0.5)),name="Hourly Salinity (Ft Myers)",
        line=list(width=1))%>%
  add_trace(x=~DATE,y=~round(Sal.30d,1),
            data=da.dat,
            color=I("forestgreen"),
            type="scatter",mode='lines+markers',name="30-day Moving Avg Salinity",
            line=list(width=3))%>%
  add_trace(x=~Date,y=~round(Data.Value,0),
            data=cal.q,color=I("black"),
            type="scatter",mode='lines+markers',name="S79 Daily Discharge",
            line=list(width=1),yaxis="y2")%>%
  add_trace(x=~Date,y=~round(Q.30,0),
            data=cal.q,color=I("indianred1"),
            type="scatter",mode='lines+markers',name="30-day Moving Avg Discharge",
            line=list(width=4),yaxis="y2")%>%
#  add_trace(x=~RECON.dates,y=~c(5,5),color=I("black"),line=list(width=4))%>%
  layout(yaxis=list(title="Salinity (PSU)",
                    # zeroline=T,
                    showline = TRUE,
                    mirror = "ticks",
                    gridcolor = toRGB("gray"),
                    gridwidth = 0.5,
                    zerolinecolor = toRGB("black"),
                    zerolinewidth = 1,
                    linecolor = toRGB("black"),
                    linewidth = 1,
                    range=c(0,30)),
         xaxis=list(title="Date",
                    zeroline=T,
                    showline = TRUE,
                    mirror = "ticks",
                    gridcolor = toRGB("gray"),
                    gridwidth = 0.5,
                    zerolinecolor = toRGB("black"),
                    zerolinewidth = 1,
                    linecolor = toRGB("black"),
                    linewidth = 1,
                    range=xlim.val.ly),
         yaxis2=list(title="Discharge (cfs)",
                     side="right",
                     zeroline=T,
                     showline = TRUE,
                     mirror = "ticks",
                     gridcolor = toRGB("black",0),
                     gridwidth = 0.5,
                     zerolinecolor = toRGB("black"),
                     zerolinewidth = 1,
                     linecolor = toRGB("black"),
                     linewidth = 1,
                     range=c(0,30000),
                     overlaying="y"),
         legend=list(bgcolor='rgba(0,0,0,0)',
                     orientation="h",
                     xanchor="center",
                     x=0.5,y=-0.15),
                    font=list(family="Times New Roman"),
         margin=list(r=80))

```

<font size=2><center>Interactive plot for Fort Myers Yacht Basin salinity (SCCF-RECON and/or SFWMD) and S79 discharge (SFWMD) data.</center></font>
<font size=3 color="red"><center>Data are provisional and subject to change.</center></font>


***

```{r Caloosa Data, include=FALSE}
End.Date=as.Date(Sys.time()); ## Update this value
Start.Date=as.Date(End.Date-duration(30,"days"));

bk.dbkeys.bot=data.frame(depth="bottom",
                         SITE=c(rep("VALI75",2),rep("FORTMYERSM",2),rep("CCORAL",2),rep("MARKH",2),rep("SANIB2",2)),
                         param=rep(c("WT","SPC"),5),
                         DBKEY=c("UL030","UL026","88288","88291","UO832","AJ012","88198","88202","WN375","WN377")                         )
sal.dat=data.frame()
for(i in 1:nrow(bk.dbkeys.bot)){
  tmp=DBHYDRO_breakpoint(Start.Date,End.Date,bk.dbkeys.bot$DBKEY[i])
  tmp$DBKEY=bk.dbkeys.bot$DBKEY[i]
  sal.dat=rbind(sal.dat,tmp)
  print(i)
}
sal.dat=merge(sal.dat,bk.dbkeys.bot,"DBKEY")
sal.dat$Date.EST=date.fun(sal.dat$DATETIME)

sal.dat.xtab=cast(sal.dat,SITE+Date.EST~param,value="Data.Value",fun.aggregate = function(x)mean(x,na.rm=T))
sal.dat.xtab$Sal=with(sal.dat.xtab,SalinityCalc(SPC,WT))

Cal.Sal=subset(sal.dat.xtab,SITE%in%c("CCORAL","FORTMYERSM","MARKH","SANIB2"))
unique(Cal.Sal$SITE)

Cal.Sal$MovingAvg.7d=with(Cal.Sal,ave(Sal,SITE,FUN=function(x) roll_meanr(x,n=7,na.rm=T)))

```

```{r Cal Instant Sal plot,echo=FALSE,fig.width=10,fig.height=5,fig.align='center'}
CALSITES=c("SANIB2","MARKH","CCORAL","FORTMYERSM","S79")
EDate.plot=as.Date(Sys.time())+duration(1,"days")
SDate.plot=as.Date(EDate.plot-duration(14,"days"))
lwd.val=1
xlim.val=as.POSIXct(strptime(c(SDate.plot,EDate.plot),"%Y-%m-%d"),tz="EST")
xmaj=seq(xlim.val[1],xlim.val[2],by="7 days");xmin=seq(xlim.val[1],xlim.val[2],by="1 days")

ylim.val=c(0,40);
ylim.val2=c(0,20);
by.y=10;ymaj=seq(ylim.val[1],ylim.val[2],by.y);ymin=seq(ylim.val[1],ylim.val[2],by.y/2)
colrmp="blue"
txt.cex=1

par(family="serif",cex.axis=1.2,mar=c(1.5,2,1,1),oma=c(2,3,4,1),mgp=c(3,1,0));
layout(matrix(c(1:4,rep(5,3),6),2,4,byrow=T),heights=c(1,0.25));

station.label=c("Sanibel","Shell Point","Cape Coral","Ft. Myers")
for(i in 1:3){
plot(Sal~Date.EST,subset(Cal.Sal,SITE==CALSITES[i]),type="n",ylim=ylim.val,xlim=xlim.val,xaxs="i",yaxs="i",ann=F,axes=F)
xx=c(xlim.val[1],xlim.val[1],xlim.val[2],xlim.val[2])
yy=c(0,5,5,0);polygon(x=xx,y=yy,col="peachpuff1")
yy2=c(35,40,40,35);polygon(x=xx,y=yy2,col="peachpuff1")
yy3=c(30,35,35,30);polygon(x=xx,y=yy3,col="khaki")
yy4=c(5,10,10,5);polygon(x=xx,y=yy4,col="khaki")
yy5=c(10,30,30,10);polygon(x=xx,y=yy5,col="darkseagreen2")
abline(h=seq(0,40,5))
with(subset(Cal.Sal,SITE==CALSITES[i]),pt_line(Date.EST,Sal,1,colrmp,2,21,colrmp,cex=2,pt.col=colrmp))
with(subset(Cal.Sal,SITE==CALSITES[i]),lines(Date.EST,MovingAvg.7d,lwd=2.5,col="orange"))
axis_fun(1,xmaj,xmin,format(xmaj,"%m/%d"),line=-0.5)
axis_fun(2,ymaj,ymin,ymaj)
mtext(side=3,station.label[i])
box(lwd=lwd.val)
if(i==1){mtext(side=2,"Salinity (PSU)",line=2,cex=1.25)}
if(i==2){mtext(expression(paste(underline("Oyster Condition"))),side=3,cex=1,line=1.75,outer=F)}
}

plot(Sal~Date.EST,subset(Cal.Sal,SITE==CALSITES[i]),type="n",ylim=ylim.val,xlim=xlim.val,xaxs="i",yaxs="i",ann=F,axes=F)
xx=c(xlim.val[1],xlim.val[1],xlim.val[2],xlim.val[2])
yy=c(0,10,10,0);polygon(x=xx,y=yy,col="darkseagreen2")
yy=c(10,15,15,10);polygon(x=xx,y=yy,col="khaki")
yy=c(15,40,40,15);polygon(x=xx,y=yy,col="peachpuff1")
abline(h=seq(0,40,5))
with(subset(Cal.Sal,SITE==CALSITES[4]),pt_line(Date.EST,Sal,1,colrmp,2,21,colrmp,cex=2,pt.col=colrmp))
with(subset(Cal.Sal,SITE==CALSITES[4]),lines(Date.EST,MovingAvg.7d,lwd=2.5,col="orange"))
axis_fun(1,xmaj,xmin,format(xmaj,"%m/%d"),line=-0.5)
axis_fun(2,ymaj,ymin,ymaj)
mtext(side=3,station.label[4])
box(lwd=lwd.val)
mtext("Month/Day",side=1,line=-6,cex=1.25,outer=T)
mtext(expression(paste(underline("Tape grass Condition"))),side=3,cex=1,line=1.75,outer=F)

plot(0:1,0:1,ann=F,axes=F,type="n")
legend(0.25,0.15,legend=c("Daily Average", "7-Day Moving Avg"),
       pch=c(21,NA),
       lty=c(NA,1),
       lwd=c(0.01,3),
       col=c("blue","orange"),
       pt.bg=c("blue",NA),
       pt.cex=1.5,ncol=1,cex=1.25,bty="n",y.intersp=1,x.intersp=0.75,xpd=NA,xjust=0.5,yjust=0.5,
       title.adj = 0,title="")
legend(0.5,0.15,legend=c("Poor(<5 or >35)","Fair (5-10 or 30-35)","Good(10-30)"),
       pch=c(22,22,22),
       lty=NA,
       lwd=0.01,
       col="black",
       pt.bg=c("peachpuff1","khaki","darkseagreen2"),
       pt.cex=2.5,ncol=1,cex=1.25,bty="n",y.intersp=1,x.intersp=0.75,xpd=NA,xjust=0.5,yjust=0.5,
       title.adj = 0,title="Oyster Salinity Condition")

plot(0:1,0:1,ann=F,axes=F,type="n")
legend(0.5,0.15,legend=c("Poor(>15)","Fair (10 - 15)","Good(<10)"),
       pch=c(22,22,22),
       lty=NA,
       lwd=0.01,
       col="black",
       pt.bg=c("peachpuff1","khaki","darkseagreen2"),
       pt.cex=2.5,ncol=1,cex=1.25,bty="n",y.intersp=1,x.intersp=0.75,xpd=NA,xjust=0.5,yjust=0.5,
       title.adj = 0,title="Tape Grass Salinity Condition")
grid.raster(logo,x=0.045,y=0.055,just=c("left","bottom"),width=unit(1.25,"inches"))
```


<font size=2><center>Daily average bottom salinity data for the last 14-days from sampling locations within the tidal Caloosahatchee River Estuary relative to oyster health (Sanibel, Shell Point and Cape Coral) and tape grass (<i>Vallisneria americana</i>) health (Ft. Myers only) conditions.</center></font>
<font size=3 color="red"><center>Data are provisional and subject to change.</center></font>
